Graphical representation example: Alternative interpretations

### 2023-11-22 notebooks/Graphical_representation_alternatives.Rmd
Versions start of "Parameters and representation" section, including the function computing the multidimensional parameters

>>>>

## Parameters and representation in the oblique space

The MDISC and the distance component of the MIL are the same in both spaces.
However, in order to represent the item in the latent space, instead of
[Equation 25][gh-eq-25], we must apply [Equation 20][gh-eq-20] to compute the
angles with the axes of the latent space. In order to that, we first need to 
redefine the function [`compute_mirt_params()`][gh-par-fun] to compute the
latent space angles instead of the test space ones:

[gh-eq-25]: https://github.com/DaniMori/mirt-parameters/blob/8fa41540ff077f07db4b87840f0acc86eb4be2ea/output/paper_draft/paper_M2PLM_parameters.Rmd#L599

[gh-eq-20]: https://github.com/DaniMori/mirt-parameters/blob/8fa41540ff077f07db4b87840f0acc86eb4be2ea/output/paper_draft/paper_M2PLM_parameters.Rmd#L532

[gh-par-fun]: https://github.com/DaniMori/mirt-parameters/blob/8fa41540ff077f07db4b87840f0acc86eb4be2ea/R/Mirt_toolbox.R#L30

```{r redefine-compute-mirt-params}
compute_mirt_params <- function(items,
                                intercept,
                                discrimination,
                                cov_matrix,
                                item_id = item,
                                dir_out = c("cos", "rad", "deg")) {
  ## Argument checking and formatting: ----

  # Enquote column selections:
  item_id        <- rlang::enquo(item_id)
  intercept      <- rlang::enquo(intercept)
  discrimination <- rlang::enquo(discrimination)

  # Check number of columns selected:

  id_col     <- items |> dplyr::select(!!item_id)
  intr_col   <- items |> dplyr::select(!!intercept)
  discr_cols <- items |> dplyr::select(!!discrimination)

  n_discr_cols <- discr_cols |> ncol()

  assertive.properties::assert_is_of_length(id_col,   1)
  assertive.properties::assert_is_of_length(intr_col, 1)

  assertive.extra::assert_is_greater_than_or_equal_to(n_discr_cols, 1)

  # Check/format covariance matrix:
  if (missing(cov_matrix)) {

    cov_matrix <- n_discr_cols |> diag()

  } else {

    dim_cov <- cov_matrix |> ncol()

    assertive.base::assert_are_identical(dim_cov, n_discr_cols)
    assertive.extra::assert_is_covariance_matrix(cov_matrix)
  }

  # Direction options:
  dir_out <- dir_out |> match.arg(several.ok = TRUE)
  one_dir <- dir_out                      |>
    assertive.properties::is_of_length(1) |>
    as.logical()

  ## Main: ----

  # Compute inverse s.d. matrix:
  var_matrix    <- cov_matrix |> diag() |> diag()
  inv_sd_matrix <- var_matrix |> sqrt() |> solve()

  items                                                                      |>
    tidyr::pivot_longer(!!discrimination, names_to = "par", values_to = "a") |>
    dplyr::group_by(!!item_id)                                               |>
    # This renaming is necessary for accessing the variable in `transmute`:
    dplyr::rename(d = !!intercept)                                           |>
    dplyr::transmute(
      !!item_id,
      ## Compute the multidimensional parameters:
      dim   = par |> stringr::str_extract("\\d+"),
      MDISC = (t(a) %*% cov_matrix %*% a) |> drop() |> sqrt(),
      D     = - d / MDISC,
      cos   = (inv_sd_matrix %*% cov_matrix %*% a / MDISC)  |> drop(),
      rad   = acos(cos),
      deg   = rad * RAD_DEG_FACTOR
    )                                                                        |>
    dplyr::ungroup()                                                         |>
    select(!!item_id, dim, MDISC, D, all_of(dir_out))                        |>
    tidyr::pivot_wider(
      names_from  = dim,
      values_from = all_of(dir_out),
      names_glue  = one_dir |> if_else('{.value}_{.name}', '{.name}')
    )
}
```
